---
title: "reworking your workflow"
subtitle: "combining data analysis and reporting with dynamic documents"
author: "Christof Neumann"
institute: "RTG Understanding Social Relationships"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    chakra: libs/remark-latest.min.js
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
editor_options: 
  chunk_output_type: console
---

```{css, echo = FALSE}
.XC .remark-code * {
  background-color: antiquewhite!important;
}
.XC2 .remark-code, .XC2 .remark-code * {
  background-color: seashell!important;
  # text-shadow: 0 0 5px #333;
}
.content-box { 
    box-sizing: border-box;
    background-color: #e2e2e2;
}
.content-box-yellow {
  box-sizing: border-box;
  border-radius: 15px;
  margin: 0 0 15px;
  overflow: hidden;
  padding: 0px 20px 0px 20px;
  width: 100%;
}
.content-box-blue { background-color: #F0F8FF; }
.content-box-yellow { background-color: #fef5c4; }

```

```{r, echo=FALSE}
check_for_package <- function(p) {
  res <- suppressMessages(suppressWarnings(require(p, character.only = TRUE)))
  res
}

make_placeholder <- function(header, missingpackage) {
  cat(paste0("## ", header, "\n\n", 
             "- didn't find package `", missingpackage, "`", "\n\n", 
             "- will not include this slide here",  "\n\n"))
}


fast_override <- TRUE

```


```{r, child="bitsandpieces/content.Rmd"}

```

---
class: inverse, center, middle

# dynamic documents

---

```{r, child="bitsandpieces/dynamic_documents.Rmd"}

```


---


```{r, eval = TRUE, child="bitsandpieces/survey_results.Rmd"}

```


---

```{r, child="bitsandpieces/background.Rmd"}

```

---
class: inverse, center, middle
# what is R markdown and why should we care?

---

```{r, child="bitsandpieces/rmarkdown_intro.Rmd"}

```

---
class: center, middle
# your most important collaborator is your future self!!! 

---

```{r, child="bitsandpieces/when_complicated.Rmd"}

```




---
class: inverse, center, middle
# the nitty and the gritty


---

```{r, child="bitsandpieces/rmarkdown_pieces.Rmd"}

```




---
class: inverse, center, middle
# getting to it


---

```{r, child="bitsandpieces/practical_0_prep.Rmd"}

```

---

```{r, child="bitsandpieces/practical_1_yaml_header.Rmd"}

```

---

```{r, child="bitsandpieces/practical_2_paragraph.Rmd"}

```

---

```{r, child="bitsandpieces/practical_3_first_chunk.Rmd"}

```

---

```{r, child="bitsandpieces/practical_4_more_chunks.Rmd"}

```

---

```{r, eval=TRUE, child="bitsandpieces/practical_5_sexpr.Rmd"}

```


---

```{r, eval=TRUE, child="bitsandpieces/practical_6_math.Rmd"}

```

---

```{r, eval=TRUE, child="bitsandpieces/practical_7_tables.Rmd"}

```

---

```{r, eval=TRUE, child="bitsandpieces/practical_8_refs.Rmd"}

```




---

## going further

- cross-references (to figures and tables)

- table and plotting options

- conditional inclusion of chunks

- actually using $\LaTeX$

- formatting (chapters)

- extended referencing (bibliographic)

- integrating other coding languages (Python, `stan`, `C++`, ...)

- put it all under version control



















---
class: inverse, center, middle

# wrapping up


---

## wrapping up

- establish good practice

--

- you can't reproduce what doesn't exist

--

- your single most important collaborator is your future self

--

- think about your workflow

```{r vince, eval = TRUE, echo=FALSE, out.width="60%", fig.align='right'}
suppressPackageStartupMessages(library(magick))
vince <- image_read("decoration_files/vince.gif") 
vince
```


