
## trouble shooting

- if you get into trouble with R not finding files, one strategy is to make rmarkdown print the current working directory, e.g. put this in your document (and set the chunk that causes the trouble to `eval = FALSE`):

- this tells you where rmarkdown thinks the working directory is

.XC[
````
```{r}`r ''`
cat(getwd())
```
````
]

```{r, eval=TRUE}
cat(getwd())
```


---

## trouble shooting

- now you can use relative navigation to find the correct file path

- for example, "`../`" navigates one level up in the folder structure

- this is not needed if you work with RStudio projects

- being within an RStudio project, usually navigation is only into subfolders

```{r, error = TRUE, eval = FALSE}
xdata <- read.csv("data_files/individual_files/file1.csv")
```

- if you really need to go the other way, it could look like this

```{r, error = TRUE, eval = FALSE}
xdata <- read.csv("../../data_files/individual_files/file1.csv")
```




---


## trouble shooting

- if a chunk results in an error, by default the document won't compile

.XC[
````
```{r}`r ''`
mean(doesntexist)
```
````
]


- if you want successful compilation anyway, there is the chunk option `error = TRUE`

.XC[
````
```{r, error = TRUE}`r ''`
mean(doesntexist)
```
````
]

```{r, error = TRUE}
mean(doesntexist)
```

